---
title: "BHealSc Curriculum Map (2022)"
#author: Simon Horsburgh
output: 
  flexdashboard::flex_dashboard:
    theme:
      bootswatch: flatly
#      css: style.css
      # base_font:
      #     google: "Open Sans"
#      navbar-bg: #003D79
      version: 4
    orientation: columns
    vertical_layout: fill
editor_options: 
  chunk_output_type: console
---

```{css, echo=FALSE}
.datatables.html-widget.html-widget-static-bound { 
  height: auto !important;
#  width: 90vw !important;
}
.dataTables_scrollBody {
  height: unset !important;
}

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
#library(knitr)
library(flexdashboard)
library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
library(htmlwidgets)
#library(networkD3)
library(tippy)
library(htmltools)
library(DT)
library(r2resize)
#library(flextable)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()

Reporting_Year <- 2022
```

```{r functions}
make_tippy <- function(letter = "a",
                       BHealSc_Outcome = " ",
                       Otago_Outcome = " ",
                       Detail = " ") {

  letter <- paste0("<p><strong>", letter, "</strong>")
  BHealSc_Outcome = paste0(BHealSc_Outcome, "  <em>", Otago_Outcome, "</em></p>")
  Detail = paste0("<span style='font-size:14px; text-align:left'><ol type='i'>", Detail, "</ol><span>")

  return(tippy(text = paste0(letter, " ", BHealSc_Outcome),
        tooltip = Detail,
        allowHTML = TRUE,
        arrow = TRUE,
        inertia = TRUE,
        interactive = TRUE,
        theme = "light")
  )
}

make_paper_summary <- function(Papers, Paper = "CMHC 201") {
  
  Papers <- Papers %>%
    filter(PaperCode == Paper)
  
  text <- paste0("<b>", Papers$PaperCode[1], "</b> <br> <i>(", Papers$PaperTitle[1], ")</i> <br> <b>Semester:</b> ", Papers$Semester[1], " <br> <b>Convenor:</b> ", Papers$Convenor[1], " <br> <b>Email:</b> ", Papers$Email[1], " <br> <b>Pre-Reqs:</b> ", Papers$PreReqs[1], " <br> <b>Restrictions:</b> ", Papers$Restrictions[1])

  sizeableCard(HTML(text))
}

make_paper_summary_outcomes <- function(Papers, Paper = "CMHC 201", Outcome_list = Outcome_list) {

  BOs <- Papers %>%
    filter(PaperCode == Paper) %>%
    select(BHealSc_Outcomes) %>%
    separate_longer_delim(BHealSc_Outcomes,
                          delim = ";") %>%
    rename(Letter = BHealSc_Outcomes) %>%
    left_join(Outcome_list, by = "Letter") %>%
    mutate(Letter = paste0("<b>", Letter, "</b> ", BHealSc_Outcome)) %>%
    select(Letter)

    sizeableCard(
      datatable(BOs,
               class = 'hover',
               rownames = FALSE,
               colnames = c("BHealSc Outcomes"),
               escape = FALSE,
               options = list(dom = 't',
                              autoWidth = TRUE,
                              ordering = FALSE,
                              pageLength = nrow(BOs)))
    )
    
}

make_paper_outcomes <- function(Papers, Paper = "CMHC 201", Outcome_list = Outcome_list) {

  Objs <- Papers %>%
      filter(PaperCode == Paper) %>%
      separate_wider_delim(cols = Objectives,
             names = c("Obj_1", "Obj_2", "Obj_3", "Obj_4", "Obj_5", "Obj_6", "Obj_7", "Obj_8", "Obj_9", "Obj_10", "Obj_11", "Obj_12", "Obj_13", "Obj_14", "Obj_15"),
             delim = ";",
             too_few = "align_start",
             cols_remove = FALSE) %>%
    replace_na(list(Obj_1 = " ",
                    Obj_2 = " ",
                    Obj_3 = " ",
                    Obj_4 = " ",
                    Obj_5 = " ",
                    Obj_6 = " ",
                    Obj_7 = " ",
                    Obj_8 = " ",
                    Obj_9 = " ",
                    Obj_10 = " ",
                    Obj_11 = " ",
                    Obj_12 = " ",
                    Obj_13 = " ",
                    Obj_14 = " ",
                    Obj_15 = " "
                    )) %>%
    pivot_longer(cols = starts_with("Obj_"),
                 values_to = "Learning_Objective") %>%
    filter(Learning_Objective != " ")

  BOs <- select(Objs, Learning_Objective, starts_with("LO_Outcomes_"))
  BOs <- BOs %>%
    mutate(LO_Num = 1:nrow(BOs)) %>%
    pivot_longer(cols = starts_with("LO_Outcomes_"),
                 values_to = "Letter") %>%
    mutate(name = str_remove(name, "LO_Outcomes_")) %>%
    filter(as.character(LO_Num) == name) %>%
    separate_longer_delim(cols = Letter,
                          delim = ";") %>%
    left_join(Outcome_list, by = "Letter") %>%
    mutate(BHealSc_Outcome = paste0("<b>", Letter, "</b> ", BHealSc_Outcome, "<br />"),
           Learning_Objective = paste0(name, ". ", Learning_Objective)) %>%
    pivot_wider(names_from = "Letter",
                values_from = "BHealSc_Outcome")
  
  tb <- BOs %>%
    select(Learning_Objective, !c(name, LO_Num))
  
  tb <- tb %>%
    select(order(colnames(tb))) %>%
    relocate(Learning_Objective) %>%
    unite(col = BHealSc_Outcome,
          any_of(c(2:ncol(tb))),
          sep = "",
          na.rm = TRUE)

  datatable(tb,
           class = 'hover stripe',
           rownames = FALSE,
           colnames = c("Learning Objectives", "BHealSc Outcomes"),
           escape = 1,
           options = list(dom = 't',
                          autoWidth = TRUE,
                          ordering = FALSE,
                          pageLength = nrow(tb)))
  
}

make_paper_assess_info <- function(Papers, Paper = "CMHC 201") {
  Assess <- Papers %>%
    filter(PaperCode == Paper) %>%
    separate_wider_delim(cols = IA_Description,
              names = c("A1", "A2", "A3", "A4", "A5", "A6", "A7", "A8", "A9", "A10"),
              delim = ";",
             too_few = "align_start",
             cols_remove = FALSE) %>%
    separate_wider_delim(cols = IA_Weight,
              names = c("W1", "W2", "W3", "W4", "W5", "W6", "W7", "W8", "W9", "W10"),
              delim = ";",
             too_few = "align_start",
             cols_remove = FALSE) %>%
    replace_na(list(A1 = " ",
                    A2 = " ",
                    A3 = " ",
                    A4 = " ",
                    A5 = " ",
                    A6 = " ",
                    A7 = " ",
                    A8 = " ",
                    A9 = " ",
                    A10 = " ",
                    W1 = " ",
                    W2 = " ",
                    W3 = " ",
                    W4 = " ",
                    W5 = " ",
                    W6 = " ",
                    W7 = " ",
                    W8 = " ",
                    W9 = " ",
                    W10 = " ",
                    IA_Details_1 = " ",
                    IA_Details_2 = " ",
                    IA_Details_3 = " ",
                    IA_Details_4 = " ",
                    IA_Details_5 = " "))
    text <- paste0("<p><strong>Paper Assessments</strong></p><table id='table_", Paper, "'><tr><th>Assessment</th><th>Details</th><th>Weight</th></tr>")

  for (i in 0:9) {
    text <- paste0(text, ifelse(Assess[1, (match("A1", names(Assess)) + i)] == " ",
                                "",
                                paste0("<tr><td>", Assess[1, (match("A1", names(Assess)) + i)], "</td><td>", Assess[1, (match("W1", names(Assess)) + i)], "</td></tr>"))
    )
  }
  text <- paste0(text, "</table><br>")

  return(text)

}

make_major_GAs_table <- function(Nodes, Major) {
  
  mat <- matrix(ncol = 17, nrow = nrow(filter(Nodes, type == TRUE)))
  mat <- as.data.frame(mat) %>%
    as_tibble() %>%
    mutate(across(everything(), as.character)) %>%
    bind_cols(select(filter(Nodes, type == TRUE), Node))
  
  names(mat) <- c(letters[1:17], "Paper")
  
  Major <- Major %>%
    mutate(Letter = str_sub(BHealSc_Outcome, 1, 1))
  
  for (i in 1:nrow(Major)) {
    mat[mat$Paper == Major$Paper[i], str_which(letters, Major$Letter[i])] <- " "
  }
  
  mat <- relocate(mat, Paper, .before = a)
  
  datatable(mat,
            class = 'compact hover stripe',
            rownames = FALSE,
            escape = FALSE,
            options = list(dom = 't',
                           ordering = FALSE,
                           pageLength = nrow(mat))) %>%
    formatStyle(colnames(mat)[2:18],
                backgroundColor = styleEqual(" ", "#91c293"),
                border = '1px solid #FFFFFF')
}

```

```{r load}
Outcomes <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                              sheet = "BHealSc Outcomes") %>%
  separate(col = Outcomes,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Outcome = paste0(BHealSc_Outcome, "\n", "Otago_Attribute"))

Map_Outcomes <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                              sheet = "BHealSc Outcomes")

CMHC <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "CMHC") %>%
  separate(col = Paper,
           into = c("Paper_Code", "Paper_Title"),
           sep = "[(]") %>%
  separate(col = `BHealSc Outcome`,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Paper_Title = paste0("(", Paper_Title),
         Paper_Code = str_remove(Paper_Code, coll("\r\n")),
         Paper = paste0("<b>", Paper_Code, "</b>\n<i>", Paper_Title, "</i>"),
         Outcome = paste0(BHealSc_Outcome, "\n<i>", Otago_Attribute, "</i>"))
         #Outcome = factor(Outcome, levels = Outcomes$Outcome))

CMHC_nodes <- c(unique(CMHC$Paper), sort(unique(CMHC$Outcome)))
CMHC_nodes <- tibble(id = seq_len(length(CMHC_nodes)), Node = CMHC_nodes) %>%
  left_join(select(CMHC, Paper, Paper_Code),
            by = c("Node" = "Paper")) %>%
  rename(label = Paper_Code) %>%
  distinct() %>%
  mutate(type = if_else(substr(Node, 1, 1) == "<", TRUE, FALSE),
         layer = if_else(substr(Node, 1, 1) == "<", 1, 2),
         label = if_else(is.na(label), substr(Node, 1, 1), label))
CMHC_edges <- CMHC %>%
  left_join(CMHC_nodes, by = c("Paper" = "Node")) %>%
  left_join(CMHC_nodes, by = c("Outcome" = "Node")) %>%
  select(from = id.x, to = id.y, label.x) %>%
  mutate(weight = 1,
         group = substr(label.x, 6, 6)) %>%
  distinct()

MAOH <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "MAOH") %>%
  separate(col = Paper,
           into = c("Paper_Code", "Paper_Title"),
           sep = "[(]") %>%
  separate(col = `BHealSc Outcome`,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Paper_Title = paste0("(", Paper_Title),
         Paper_Code = str_remove(Paper_Code, coll("\r\n")),
         Paper = paste0("<b>", Paper_Code, "</b>\n<i>", Paper_Title, "</i>"),
         Outcome = paste0(BHealSc_Outcome, "\n<i>", Otago_Attribute, "</i>"))

MAOH_nodes <- c(unique(MAOH$Paper), sort(unique(MAOH$Outcome)))
MAOH_nodes <- tibble(id = seq_len(length(MAOH_nodes)), Node = MAOH_nodes) %>%
  left_join(select(MAOH, Paper, Paper_Code),
            by = c("Node" = "Paper")) %>%
  rename(label = Paper_Code) %>%
  distinct() %>%
  mutate(type = if_else(substr(Node, 1, 1) == "<", TRUE, FALSE),
         layer = if_else(substr(Node, 1, 1) == "<", 1, 2),
         label = if_else(is.na(label), substr(Node, 1, 1), label))
MAOH_edges <- MAOH %>%
  left_join(MAOH_nodes, by = c("Paper" = "Node")) %>%
  left_join(MAOH_nodes, by = c("Outcome" = "Node")) %>%
  select(from = id.x, to = id.y, label.x) %>%
  mutate(weight = 1,
         group = substr(label.x, 6, 6)) %>%
  distinct()

PACH <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "PACH") %>%
  separate(col = Paper,
           into = c("Paper_Code", "Paper_Title"),
           sep = "[(]") %>%
  separate(col = `BHealSc Outcome`,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Paper_Title = paste0("(", Paper_Title),
         Paper_Code = str_remove(Paper_Code, coll("\r\n")),
         Paper = paste0("<b>", Paper_Code, "</b>\n<i>", Paper_Title, "</i>"),
         Outcome = paste0(BHealSc_Outcome, "\n<i>", Otago_Attribute, "</i>"))

PACH_nodes <- c(unique(PACH$Paper), sort(unique(PACH$Outcome)))
PACH_nodes <- tibble(id = seq_len(length(PACH_nodes)), Node = PACH_nodes) %>%
  left_join(select(PACH, Paper, Paper_Code),
            by = c("Node" = "Paper")) %>%
  rename(label = Paper_Code) %>%
  distinct() %>%
  mutate(type = if_else(substr(Node, 1, 1) == "<", TRUE, FALSE),
         layer = if_else(substr(Node, 1, 1) == "<", 1, 2),
         label = if_else(is.na(label), substr(Node, 1, 1), label))
PACH_edges <- PACH %>%
  left_join(PACH_nodes, by = c("Paper" = "Node")) %>%
  left_join(PACH_nodes, by = c("Outcome" = "Node")) %>%
  select(from = id.x, to = id.y, label.x) %>%
  mutate(weight = 1,
         group = substr(label.x, 6, 6)) %>%
  distinct()

PUBH <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "PUBH") %>%
  separate(col = Paper,
           into = c("Paper_Code", "Paper_Title"),
           sep = "[(]") %>%
  separate(col = `BHealSc Outcome`,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Paper_Title = paste0("(", Paper_Title),
         Paper_Code = str_remove(Paper_Code, coll("\r\n")),
         Paper = paste0("<b>", Paper_Code, "</b>\n<i>", Paper_Title, "</i>"),
         Outcome = paste0(BHealSc_Outcome, "\n<i>", Otago_Attribute, "</i>"))

PUBH_nodes <- c(unique(PUBH$Paper), sort(unique(PUBH$Outcome)))
PUBH_nodes <- tibble(id = seq_len(length(PUBH_nodes)), Node = PUBH_nodes) %>%
  left_join(select(PUBH, Paper, Paper_Code),
            by = c("Node" = "Paper")) %>%
  rename(label = Paper_Code) %>%
  distinct() %>%
  mutate(type = if_else(substr(Node, 1, 1) == "<", TRUE, FALSE),
         layer = if_else(substr(Node, 1, 1) == "<", 1, 2),
         label = if_else(is.na(label), substr(Node, 1, 1), label))
PUBH_edges <- PUBH %>%
  left_join(PUBH_nodes, by = c("Paper" = "Node")) %>%
  left_join(PUBH_nodes, by = c("Outcome" = "Node")) %>%
  select(from = id.x, to = id.y, label.x) %>%
  mutate(weight = 1,
         group = substr(label.x, 6, 6)) %>%
  distinct()



Papers <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "Papers") %>% 
  filter(Year == Reporting_Year) %>%
  mutate(across(starts_with("IA_Details_"), .fns = as.character))

Outcome_list <- Outcomes %>%
  mutate(BHealSc = str_sub(BHealSc_Outcome, start = 3)) %>%
  select(Letter, BHealSc_Outcome = BHealSc)
```

# List of Degree Attributes {data-navmenu="Graduate Attributes"}  

```{r List_of_GAs, results = 'asis'}

GAs <- tribble(~letter, ~BHealSc_Outcome, ~OA, ~AD)

for (i in 1:nrow(Outcomes)) {
  GAs <- add_row(GAs, letter = Outcomes$Letter[i],
                      BHealSc_Outcome = Outcomes$BHealSc_Outcome[i],
                      OA = Outcomes$Otago_Attribute[i],
                      AD = Outcomes$Detail[i]
  )
}

GAs <- GAs %>%
  mutate(BHealSc_Outcome = str_sub(BHealSc_Outcome, 3),
         OA = str_sub(OA, start = 2, end = -2),
         AD = paste0("<par><ol type='i'>", AD, "</ol></par>"))

datatable(GAs,
          class = 'compact hover stripe',
          rownames = FALSE,
          colnames = c("", "BHealSc\n Outcome", "Otago\n Graduate Attribute", "Details"),
          escape = c(1:3),
          options = list(dom = 't',
                         autoWidth = TRUE,
                         ordering = FALSE,
                         pageLength = nrow(GAs))) %>%
  formatStyle(1, fontWeight = "bold")

```



# Map By Major {data-navmenu="Graduate Attributes"}  

## Column {data-width=600 .tabset}       

### Community Health Care  

> **Graduate Attributes by Paper** <br /> *All listed papers must be passed as part of the major*    
  
```{r CMHC}
make_major_GAs_table(Nodes = CMHC_nodes, Major = CMHC)

```  

### MÄori Health     

> **Graduate Attributes by Paper** <br /> *All listed papers must be passed as part of the major*    
  
```{r MAOH}
make_major_GAs_table(Nodes = MAOH_nodes, Major = MAOH)

```

### Pacific and Global Health     

> **Graduate Attributes by Paper** <br /> *All listed papers must be passed as part of the major*    
  
```{r PACH}
make_major_GAs_table(Nodes = PACH_nodes, Major = PACH)

```

### Public Health      

> **Graduate Attributes by Paper** <br /> *All listed papers must be passed as part of the major, although only one of PUBH 304 or PUBH 311 is required*    
  
```{r PUBH}
make_major_GAs_table(Nodes = PUBH_nodes, Major = PUBH)

```

## Column {data-width=400 .tabset}  

### **Graduate Profile**     

> *Otago Graduate Attributes in Italics*  

```{r Outcomes}

make_tippy(letter = Map_Outcomes$Letter[1],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[1],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[1],
             Detail = Map_Outcomes$Detail[1])

make_tippy(letter = Map_Outcomes$Letter[2],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[2],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[2],
             Detail = Map_Outcomes$Detail[2])


make_tippy(letter = Map_Outcomes$Letter[3],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[3],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[3],
             Detail = Map_Outcomes$Detail[3])


make_tippy(letter = Map_Outcomes$Letter[4],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[4],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[4],
             Detail = Map_Outcomes$Detail[4])


make_tippy(letter = Map_Outcomes$Letter[5],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[5],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[5],
             Detail = Map_Outcomes$Detail[5])


make_tippy(letter = Map_Outcomes$Letter[6],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[6],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[6],
             Detail = Map_Outcomes$Detail[6])


make_tippy(letter = Map_Outcomes$Letter[7],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[7],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[7],
             Detail = Map_Outcomes$Detail[7])


make_tippy(letter = Map_Outcomes$Letter[8],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[8],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[8],
             Detail = Map_Outcomes$Detail[8])


make_tippy(letter = Map_Outcomes$Letter[9],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[9],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[9],
             Detail = Map_Outcomes$Detail[9])


make_tippy(letter = Map_Outcomes$Letter[10],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[10],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[10],
             Detail = Map_Outcomes$Detail[10])


make_tippy(letter = Map_Outcomes$Letter[11],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[11],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[11],
             Detail = Map_Outcomes$Detail[11])


make_tippy(letter = Map_Outcomes$Letter[12],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[12],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[12],
             Detail = Map_Outcomes$Detail[12])


make_tippy(letter = Map_Outcomes$Letter[13],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[13],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[13],
             Detail = Map_Outcomes$Detail[13])


make_tippy(letter = Map_Outcomes$Letter[14],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[14],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[14],
             Detail = Map_Outcomes$Detail[14])


make_tippy(letter = Map_Outcomes$Letter[15],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[15],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[15],
             Detail = Map_Outcomes$Detail[15])


make_tippy(letter = Map_Outcomes$Letter[16],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[16],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[16],
             Detail = Map_Outcomes$Detail[16])


make_tippy(letter = Map_Outcomes$Letter[17],
             BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[17],
             Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[17],
             Detail = Map_Outcomes$Detail[17])
```


<!-- Column {data-width=300} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### **Graduate Profile**   -->

<!-- ```{r Outcomes} -->

<!-- make_tippy(letter = Map_Outcomes$Letter[1], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[1], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[1], -->
<!--              Detail = Map_Outcomes$Detail[1]) -->

<!-- make_tippy(letter = Map_Outcomes$Letter[2], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[2], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[2], -->
<!--              Detail = Map_Outcomes$Detail[2]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[3], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[3], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[3], -->
<!--              Detail = Map_Outcomes$Detail[3]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[4], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[4], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[4], -->
<!--              Detail = Map_Outcomes$Detail[4]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[5], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[5], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[5], -->
<!--              Detail = Map_Outcomes$Detail[5]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[6], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[6], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[6], -->
<!--              Detail = Map_Outcomes$Detail[6]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[7], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[7], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[7], -->
<!--              Detail = Map_Outcomes$Detail[7]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[8], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[8], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[8], -->
<!--              Detail = Map_Outcomes$Detail[8]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[9], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[9], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[9], -->
<!--              Detail = Map_Outcomes$Detail[9]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[10], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[10], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[10], -->
<!--              Detail = Map_Outcomes$Detail[10]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[11], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[11], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[11], -->
<!--              Detail = Map_Outcomes$Detail[11]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[12], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[12], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[12], -->
<!--              Detail = Map_Outcomes$Detail[12]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[13], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[13], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[13], -->
<!--              Detail = Map_Outcomes$Detail[13]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[14], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[14], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[14], -->
<!--              Detail = Map_Outcomes$Detail[14]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[15], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[15], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[15], -->
<!--              Detail = Map_Outcomes$Detail[15]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[16], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[16], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[16], -->
<!--              Detail = Map_Outcomes$Detail[16]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[17], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[17], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[17], -->
<!--              Detail = Map_Outcomes$Detail[17]) -->
<!-- ``` -->

# **`r Papers$PaperCode[1]`** _(`r Papers$PaperTitle[1]`)_ {data-navmenu="Paper Information"}

## Column {.tabset}  

### Paper Summary  

```{r CMHC201_Paper_Summary}
make_paper_summary(Papers, "CMHC 201")
```

```{r CMHC201_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "CMHC 201", Outcome_list = Outcome_list)

```

```{r CMHC201_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "CMHC 201", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "CMHC 201")
```

### Learning Objectives to Outcomes Map  

`r text`  

### Assessment Information  

# **`r Papers$PaperCode[2]`** _(`r Papers$PaperTitle[2]`)_ {data-navmenu="Paper Information"}

## Column {.tabset}  

### Paper Summary  

```{r CMHC211_Paper_Summary}
make_paper_summary(Papers, "CMHC 211")
```

```{r CMHC211_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "CMHC 211", Outcome_list = Outcome_list)

```

```{r CMHC211_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "CMHC 211", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "CMHC 211")
```
### Learning Objectives to Outcomes Map  

`r text`  

### Assessment Information  

# **`r Papers$PaperCode[3]`** _(`r Papers$PaperTitle[3]`)_ {data-navmenu="Paper Information"}

## Column {.tabset}  

### Paper Summary  

```{r CMHC301_Paper_Summary}
make_paper_summary(Papers, "CMHC 301")
```

```{r CMHC301_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "CMHC 301", Outcome_list = Outcome_list)

```

```{r CMHC301_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "CMHC 301", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "CMHC 301")
```

### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[4]`** _(`r Papers$PaperTitle[4]`)_ {data-navmenu="Paper Information"}

## Column {.tabset}  

### Paper Summary  

```{r CMHC311_Paper_Summary}
make_paper_summary(Papers, "CMHC 311")
```

```{r CMHC311_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "CMHC 311", Outcome_list = Outcome_list)

```

```{r CMHC311_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "CMHC 311", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "CMHC 311")
```

### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[5]`** _(`r Papers$PaperTitle[5]`)_ {data-navmenu="Paper Information"}

## Column {.tabset}  

### Paper Summary  

```{r MAOH201_Paper_Summary}
make_paper_summary(Papers, "MAOH 201")
```

```{r MAOH201_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "MAOH 201", Outcome_list = Outcome_list)

```

```{r MAOH201_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "MAOH 201", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "MAOH 201")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[6]`** _(`r Papers$PaperTitle[6]`)_ {data-navmenu="Paper Information"}  

## Column {.tabset}  

### Paper Summary  

```{r MAOH301_Paper_Summary}
make_paper_summary(Papers, "MAOH 301")
```

```{r MAOH301_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "MAOH 301", Outcome_list = Outcome_list)

```
```{r MAOH301_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "MAOH 301", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "MAOH 301")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[7]`** _(`r Papers$PaperTitle[7]`)_ {data-navmenu="Paper Information"}

## Column {.tabset}  

### Paper Summary  

```{r PACH201_Paper_Summary}
make_paper_summary(Papers, "PACH 201")
```

```{r PACH201_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "PACH 201", Outcome_list = Outcome_list)

```
```{r PACH201_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "PACH 201", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "PACH 201")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[8]`** _(`r Papers$PaperTitle[8]`)_ {data-navmenu="Paper Information"}

## Column {.tabset}  

### Paper Summary  

```{r PACH301_Paper_Summary}
make_paper_summary(Papers, "PACH 301")
```

```{r PACH301_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "PACH 301", Outcome_list = Outcome_list)

```

```{r PACH301_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "PACH 301", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "PACH 301")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[9]`** _(`r Papers$PaperTitle[9]`)_ {data-navmenu="Paper Information"}  

## Column {.tabset}  

### Paper Summary  

```{r PUBH202_Paper_Summary}
make_paper_summary(Papers, "PUBH 202")
```

```{r PUBH202_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "PUBH 202", Outcome_list = Outcome_list)

```

```{r PUBH202_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "PUBH 202", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 202")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[10]`** _(`r Papers$PaperTitle[10]`)_ {data-navmenu="Paper Information"}  

## Column {.tabset}  

### Paper Summary  

```{r PUBH203_Paper_Summary}
make_paper_summary(Papers, "PUBH 203")
```

```{r PUBH203_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "PUBH 203", Outcome_list = Outcome_list)

```

```{r PUBH203_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "PUBH 203", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 203")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[11]`** _(`r Papers$PaperTitle[11]`)_ {data-navmenu="Paper Information"}  

## Column {.tabset}  

### Paper Summary  

```{r PUBH204_Paper_Summary}
make_paper_summary(Papers, "PUBH 204")
```

```{r PUBH204_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "PUBH 204", Outcome_list = Outcome_list)

```

```{r PUBH204_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "PUBH 204", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 204")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[12]`** _(`r Papers$PaperTitle[12]`)_ {data-navmenu="Paper Information"}

## Column {.tabset}  

### Paper Summary  

```{r PUBH211_Paper_Summary}
make_paper_summary(Papers, "PUBH 211")
```

```{r PUBH211_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "PUBH 211", Outcome_list = Outcome_list)

```

```{r PUBH211_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "PUBH 211", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 204")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[13]`** _(`r Papers$PaperTitle[13]`)_ {data-navmenu="Paper Information"}

## Column {.tabset}  

### Paper Summary  

```{r PUBH303_Paper_Summary}
make_paper_summary(Papers, "PUBH 303")
```

```{r PUBH303_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "PUBH 303", Outcome_list = Outcome_list)

```

```{r PUBH303_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "PUBH 303", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 303")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[14]`** _(`r Papers$PaperTitle[14]`)_ {data-navmenu="Paper Information"}  

## Column {.tabset}  

### Paper Summary  

```{r PUBH304_Paper_Summary}
make_paper_summary(Papers, "PUBH 304")
```

```{r PUBH304_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "PUBH 304", Outcome_list = Outcome_list)

```

```{r PUBH304_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "PUBH 304", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 304")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

# **`r Papers$PaperCode[15]`** _(`r Papers$PaperTitle[15]`)_ {data-navmenu="Paper Information"}  

## Column {.tabset}  

### Paper Summary  

```{r PUBH311_Paper_Summary}
make_paper_summary(Papers, "PUBH 311")
```

```{r PUBH311_BHealSc_Outcomes}
make_paper_summary_outcomes(Papers, "PUBH 311", Outcome_list = Outcome_list)

```

```{r PUBH311_Paper_Learning_Objectives}
text <- make_paper_outcomes(Papers = Papers, Paper = "PUBH 311", Outcome_list = Outcome_list)
# assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 311")
```


### Learning Objectives to Outcomes Map  
`r text`  

### Assessment Information  

