---
title: "BHealSc Curriculum Map (2022)"
#author: Simon Horsburgh
output: 
  flexdashboard::flex_dashboard:
    theme:
      bootswatch: flatly
#      css: style.css
      # base_font:
      #     google: "Open Sans"
#      navbar-bg: #003D79
      version: 4
      # base_font:
      #   google: Prompt
      # code_font:
        # google: JetBrains Mono
    orientation: columns
    vertical_layout: fill
editor_options: 
  chunk_output_type: console
---
 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
#library(knitr)
library(flexdashboard)
library(readxl)
library(dplyr)
library(tidyr)
library(stringr)
library(htmlwidgets)
#library(networkD3)
library(tippy)
library(htmltools)
library(DT)
#library(flextable)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()

Reporting_Year <- 2022
```

```{r functions}
make_tippy <- function(letter = "a",
                       BHealSc_Outcome = " ",
                       Otago_Outcome = " ",
                       Detail = " ") {

  letter <- paste0("<p><strong>", letter, "</strong>")
  BHealSc_Outcome = paste0(BHealSc_Outcome, "  <em>", Otago_Outcome, "</em></p>")
  Detail = paste0("<span style='font-size:14px; text-align:left'><ol type='i'>", Detail, "</ol><span>")

  return(tippy(text = paste0(letter, " ", BHealSc_Outcome),
        tooltip = Detail,
        allowHTML = TRUE,
        arrow = TRUE,
        inertia = TRUE,
        interactive = TRUE,
        theme = "light")
  )
}

make_paper_info <- function(Papers, Paper = "CMHC 201") {

  Objs <- Papers %>%
      filter(PaperCode == Paper) %>%
      separate(col = Objectives,
             into = c("O1", "O2", "O3", "O4", "O5", "O6", "O7", "O8", "O9", "O10", "O11", "O12", "O13", "O14", "O15"),
             sep = ";",
             remove = FALSE) %>%
    replace_na(list(O1 = " ",
                    O2 = " ",
                    O3 = " ",
                    O4 = " ",
                    O5 = " ",
                    O6 = " ",
                    O7 = " ",
                    O8 = " ",
                    O9 = " ",
                    O10 = " ",
                    O11 = " ",
                    O12 = " ",
                    O13 = " ",
                    O14 = " ",
                    O15 = " "
                    ))

  text <- paste0("<p><strong>Learning Objectives</strong></p><ol type='1'>")
  for (i in 0:14) {
    text <- paste0(text, ifelse(Objs[1, (match("O1", names(Objs)) + i)] == " ",
                                "",
                                paste0("<li>", Objs[1, (match("O1", names(Objs)) + i)], "</li>"))
    )
  }
  text <- paste0(text, "</ol><br>")

  return(text)
}

make_paper_assess_info <- function(Papers, Paper = "CMHC 201") {
  Assess <- Papers %>%
    filter(PaperCode == Paper) %>%
    separate(col = IA_Description,
              into = c("A1", "A2", "A3", "A4", "A5", "A6", "A7", "A8", "A9", "A10"),
              sep = ";",
              remove = FALSE) %>%
    separate(col = IA_Weight,
              into = c("W1", "W2", "W3", "W4", "W5", "W6", "W7", "W8", "W9", "W10"),
              sep = ";",
              remove = FALSE) %>%
    replace_na(list(A1 = " ",
                    A2 = " ",
                    A3 = " ",
                    A4 = " ",
                    A5 = " ",
                    A6 = " ",
                    A7 = " ",
                    A8 = " ",
                    A9 = " ",
                    A10 = " ",
                    W1 = " ",
                    W2 = " ",
                    W3 = " ",
                    W4 = " ",
                    W5 = " ",
                    W6 = " ",
                    W7 = " ",
                    W8 = " ",
                    W9 = " ",
                    W10 = " "))
    text <- paste0("<p><strong>Paper Assessments</strong></p><table id='table_", Paper, "'><tr><th>Assessment</th><th>Weight</th></tr>")

  for(i in 0:9) {
    text <- paste0(text, ifelse(Assess[1, (match("A1", names(Assess)) + i)] == " ",
                                "",
                                paste0("<tr><td>", Assess[1, (match("A1", names(Assess)) + i)], "</td><td>", Assess[1, (match("W1", names(Assess)) + i)], "</td></tr>"))
    )
  }
  text <- paste0(text, "</table><br>")

  return(text)

}

make_major_GAs_table <- function(Nodes, Major) {
  
  mat <- matrix(ncol = 17, nrow = nrow(filter(Nodes, type == TRUE)))
  mat <- as.data.frame(mat) %>%
    as_tibble() %>%
    mutate(across(everything(), as.character)) %>%
    bind_cols(select(filter(Nodes, type == TRUE), Node))
  
  names(mat) <- c(letters[1:17], "Paper")
  
  Major <- Major %>%
    mutate(Letter = str_sub(BHealSc_Outcome, 1, 1))
  
  for (i in 1:nrow(Major)) {
    mat[mat$Paper == Major$Paper[i], str_which(letters, Major$Letter[i])] <- " "
  }
  
  mat <- relocate(mat, Paper, .before = a)
  
  datatable(mat,
            extensions = "Buttons",
            class = 'hover stripe',
            rownames = FALSE,
            escape = FALSE,
            options = list(dom = 't',
                           ordering = FALSE,
                           buttons = c('pdf', 'print'),
                           pageLength = nrow(mat))) %>%
    formatStyle(colnames(mat)[2:18],
                backgroundColor = styleEqual(" ", "#91c293"),
                border = '1px solid #FFFFFF')
}

```

```{r load}
Outcomes <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                              sheet = "BHealSc Outcomes") %>%
  separate(col = Outcomes,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Outcome = paste0(BHealSc_Outcome, "\n", "Otago_Attribute"))

Map_Outcomes <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                              sheet = "BHealSc Outcomes")

CMHC <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "CMHC") %>%
  separate(col = Paper,
           into = c("Paper_Code", "Paper_Title"),
           sep = "[(]") %>%
  separate(col = `BHealSc Outcome`,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Paper_Title = paste0("(", Paper_Title),
         Paper_Code = str_remove(Paper_Code, coll("\r\n")),
         Paper = paste0("<b>", Paper_Code, "</b>\n<i>", Paper_Title, "</i>"),
         Outcome = paste0(BHealSc_Outcome, "\n<i>", Otago_Attribute, "</i>"))
         #Outcome = factor(Outcome, levels = Outcomes$Outcome))

CMHC_nodes <- c(unique(CMHC$Paper), sort(unique(CMHC$Outcome)))
CMHC_nodes <- tibble(id = seq_len(length(CMHC_nodes)), Node = CMHC_nodes) %>%
  left_join(select(CMHC, Paper, Paper_Code),
            by = c("Node" = "Paper")) %>%
  rename(label = Paper_Code) %>%
  distinct() %>%
  mutate(type = if_else(substr(Node, 1, 1) == "<", TRUE, FALSE),
         layer = if_else(substr(Node, 1, 1) == "<", 1, 2),
         label = if_else(is.na(label), substr(Node, 1, 1), label))
CMHC_edges <- CMHC %>%
  left_join(CMHC_nodes, by = c("Paper" = "Node")) %>%
  left_join(CMHC_nodes, by = c("Outcome" = "Node")) %>%
  select(from = id.x, to = id.y, label.x) %>%
  mutate(weight = 1,
         group = substr(label.x, 6, 6)) %>%
  distinct()

MAOH <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "MAOH") %>%
  separate(col = Paper,
           into = c("Paper_Code", "Paper_Title"),
           sep = "[(]") %>%
  separate(col = `BHealSc Outcome`,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Paper_Title = paste0("(", Paper_Title),
         Paper_Code = str_remove(Paper_Code, coll("\r\n")),
         Paper = paste0("<b>", Paper_Code, "</b>\n<i>", Paper_Title, "</i>"),
         Outcome = paste0(BHealSc_Outcome, "\n<i>", Otago_Attribute, "</i>"))

MAOH_nodes <- c(unique(MAOH$Paper), sort(unique(MAOH$Outcome)))
MAOH_nodes <- tibble(id = seq_len(length(MAOH_nodes)), Node = MAOH_nodes) %>%
  left_join(select(MAOH, Paper, Paper_Code),
            by = c("Node" = "Paper")) %>%
  rename(label = Paper_Code) %>%
  distinct() %>%
  mutate(type = if_else(substr(Node, 1, 1) == "<", TRUE, FALSE),
         layer = if_else(substr(Node, 1, 1) == "<", 1, 2),
         label = if_else(is.na(label), substr(Node, 1, 1), label))
MAOH_edges <- MAOH %>%
  left_join(MAOH_nodes, by = c("Paper" = "Node")) %>%
  left_join(MAOH_nodes, by = c("Outcome" = "Node")) %>%
  select(from = id.x, to = id.y, label.x) %>%
  mutate(weight = 1,
         group = substr(label.x, 6, 6)) %>%
  distinct()

PACH <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "PACH") %>%
  separate(col = Paper,
           into = c("Paper_Code", "Paper_Title"),
           sep = "[(]") %>%
  separate(col = `BHealSc Outcome`,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Paper_Title = paste0("(", Paper_Title),
         Paper_Code = str_remove(Paper_Code, coll("\r\n")),
         Paper = paste0("<b>", Paper_Code, "</b>\n<i>", Paper_Title, "</i>"),
         Outcome = paste0(BHealSc_Outcome, "\n<i>", Otago_Attribute, "</i>"))

PACH_nodes <- c(unique(PACH$Paper), sort(unique(PACH$Outcome)))
PACH_nodes <- tibble(id = seq_len(length(PACH_nodes)), Node = PACH_nodes) %>%
  left_join(select(PACH, Paper, Paper_Code),
            by = c("Node" = "Paper")) %>%
  rename(label = Paper_Code) %>%
  distinct() %>%
  mutate(type = if_else(substr(Node, 1, 1) == "<", TRUE, FALSE),
         layer = if_else(substr(Node, 1, 1) == "<", 1, 2),
         label = if_else(is.na(label), substr(Node, 1, 1), label))
PACH_edges <- PACH %>%
  left_join(PACH_nodes, by = c("Paper" = "Node")) %>%
  left_join(PACH_nodes, by = c("Outcome" = "Node")) %>%
  select(from = id.x, to = id.y, label.x) %>%
  mutate(weight = 1,
         group = substr(label.x, 6, 6)) %>%
  distinct()

PUBH <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "PUBH") %>%
  separate(col = Paper,
           into = c("Paper_Code", "Paper_Title"),
           sep = "[(]") %>%
  separate(col = `BHealSc Outcome`,
           into = c("BHealSc_Outcome", "Otago_Attribute"),
           sep = "\r\n") %>%
  mutate(Paper_Title = paste0("(", Paper_Title),
         Paper_Code = str_remove(Paper_Code, coll("\r\n")),
         Paper = paste0("<b>", Paper_Code, "</b>\n<i>", Paper_Title, "</i>"),
         Outcome = paste0(BHealSc_Outcome, "\n<i>", Otago_Attribute, "</i>"))

PUBH_nodes <- c(unique(PUBH$Paper), sort(unique(PUBH$Outcome)))
PUBH_nodes <- tibble(id = seq_len(length(PUBH_nodes)), Node = PUBH_nodes) %>%
  left_join(select(PUBH, Paper, Paper_Code),
            by = c("Node" = "Paper")) %>%
  rename(label = Paper_Code) %>%
  distinct() %>%
  mutate(type = if_else(substr(Node, 1, 1) == "<", TRUE, FALSE),
         layer = if_else(substr(Node, 1, 1) == "<", 1, 2),
         label = if_else(is.na(label), substr(Node, 1, 1), label))
PUBH_edges <- PUBH %>%
  left_join(PUBH_nodes, by = c("Paper" = "Node")) %>%
  left_join(PUBH_nodes, by = c("Outcome" = "Node")) %>%
  select(from = id.x, to = id.y, label.x) %>%
  mutate(weight = 1,
         group = substr(label.x, 6, 6)) %>%
  distinct()



Papers <- read_xlsx(path = "./2022 Major - Papers - Outcome Map.xlsx",
                          sheet = "Papers") %>% 
  filter(Year == Reporting_Year)
```

# List of Degree Attributes {data-navmenu="Graduate Attributes"}  

```{r List_of_GAs, results = 'asis'}

GAs <- tribble(~letter, ~BHealSc_Outcome, ~OA, ~AD)

for (i in 1:nrow(Outcomes)) {
  GAs <- add_row(GAs, letter = Outcomes$Letter[i],
                      BHealSc_Outcome = Outcomes$BHealSc_Outcome[i],
                      OA = Outcomes$Otago_Attribute[i],
                      AD = Outcomes$Detail[i]
  )
}

GAs <- GAs %>%
  mutate(BHealSc_Outcome = str_sub(BHealSc_Outcome, 3),
         OA = str_sub(OA, start = 2, end = -2),
         AD = paste0("<par><ol type='i'>", AD, "</ol></par>"))

datatable(GAs,
          class = 'compact hover stripe',
          rownames = FALSE,
          colnames = c("", "BHealSc\n Outcome", "Otago\n Graduate Attribute", "Details"),
          escape = c(1:3),
          options = list(dom = 't',
                         ordering = FALSE,
                         pageLength = nrow(GAs))) %>%
  formatStyle(1, fontWeight = "bold")

```



# Community Health Care {data-navmenu="Graduate Attributes"}  

## Column   

### **Graduate Attributes by Paper** {.data-width=500}  

```{r CMHC}
make_major_GAs_table(Nodes = CMHC_nodes, Major = CMHC)

```

### **Specific Graduate Attributes**     

# Māori Health {data-navmenu="Graduate Attributes"}   

```{r MAOH}
make_major_GAs_table(Nodes = MAOH_nodes, Major = MAOH)

```

# Pacific and Global Health {data-navmenu="Graduate Attributes"}   

```{r PACH}
make_major_GAs_table(Nodes = PACH_nodes, Major = PACH)

```

### Public Health {data-navmenu="Graduate Attributes"}    

```{r PUBH}
make_major_GAs_table(Nodes = PUBH_nodes, Major = PUBH)

```

<!-- Column {data-width=300} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### **Graduate Profile**   -->

<!-- ```{r Outcomes} -->

<!-- make_tippy(letter = Map_Outcomes$Letter[1], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[1], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[1], -->
<!--              Detail = Map_Outcomes$Detail[1]) -->

<!-- make_tippy(letter = Map_Outcomes$Letter[2], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[2], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[2], -->
<!--              Detail = Map_Outcomes$Detail[2]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[3], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[3], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[3], -->
<!--              Detail = Map_Outcomes$Detail[3]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[4], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[4], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[4], -->
<!--              Detail = Map_Outcomes$Detail[4]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[5], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[5], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[5], -->
<!--              Detail = Map_Outcomes$Detail[5]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[6], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[6], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[6], -->
<!--              Detail = Map_Outcomes$Detail[6]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[7], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[7], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[7], -->
<!--              Detail = Map_Outcomes$Detail[7]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[8], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[8], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[8], -->
<!--              Detail = Map_Outcomes$Detail[8]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[9], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[9], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[9], -->
<!--              Detail = Map_Outcomes$Detail[9]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[10], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[10], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[10], -->
<!--              Detail = Map_Outcomes$Detail[10]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[11], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[11], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[11], -->
<!--              Detail = Map_Outcomes$Detail[11]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[12], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[12], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[12], -->
<!--              Detail = Map_Outcomes$Detail[12]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[13], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[13], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[13], -->
<!--              Detail = Map_Outcomes$Detail[13]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[14], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[14], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[14], -->
<!--              Detail = Map_Outcomes$Detail[14]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[15], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[15], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[15], -->
<!--              Detail = Map_Outcomes$Detail[15]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[16], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[16], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[16], -->
<!--              Detail = Map_Outcomes$Detail[16]) -->


<!-- make_tippy(letter = Map_Outcomes$Letter[17], -->
<!--              BHealSc_Outcome = Map_Outcomes$BHealSc_Outcome[17], -->
<!--              Otago_Outcome = Map_Outcomes$Otago_Graduate_Profile[17], -->
<!--              Detail = Map_Outcomes$Detail[17]) -->
<!-- ``` -->

Paper Information {.storyboard}
==================

### **`r Papers$PaperCode[1]`** <br> _(`r Papers$PaperTitle[1]`)_ <br> **Semester:** `r Papers$Semester[1]` <br> **Convenor:** `r Papers$Convenor[1]` <br> **Email:** `r Papers$Email[1]` <br> **Pre-Reqs:** `r Papers$PreReqs[1]` <br> **Restrictions:** `r Papers$Restrictions[1]`  

```{r CMHC201_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "CMHC 201")
assess <- make_paper_assess_info(Papers = Papers, Paper = "CMHC 201")
```

`r text`  

-------------------------------------  
`r assess`  


### **`r Papers$PaperCode[2]`** <br> _(`r Papers$PaperTitle[2]`)_ <br> **Semester:** `r Papers$Semester[2]` <br> **Convenor:** `r Papers$Convenor[2]` <br> **Email:** `r Papers$Email[2]` <br> **Pre-Reqs:** `r Papers$PreReqs[2]` <br> **Restrictions:** `r Papers$Restrictions[2]`  

```{r CMHC211_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "CMHC 211")
assess <- make_paper_assess_info(Papers = Papers, Paper = "CMHC 211")
```
`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[3]`** <br> _(`r Papers$PaperTitle[3]`)_ <br> **Semester:** `r Papers$Semester[3]` <br> **Convenor:** `r Papers$Convenor[3]` <br> **Email:** `r Papers$Email[3]` <br> **Pre-Reqs:** `r Papers$PreReqs[3]` <br> **Restrictions:** `r Papers$Restrictions[3]`  

```{r CMHC301_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "CMHC 301")
assess <- make_paper_assess_info(Papers = Papers, Paper = "CMHC 301")
```

`r text`  

-------------------------------------  
`r assess`  


### **`r Papers$PaperCode[4]`** <br> _(`r Papers$PaperTitle[4]`)_ <br> **Semester:** `r Papers$Semester[4]` <br> **Convenor:** `r Papers$Convenor[4]` <br> **Email:** `r Papers$Email[4]` <br> **Pre-Reqs:** `r Papers$PreReqs[4]` <br> **Restrictions:** `r Papers$Restrictions[4]`  


```{r CMHC311_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "CMHC 311")
assess <- make_paper_assess_info(Papers = Papers, Paper = "CMHC 311")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[5]`** <br> _(`r Papers$PaperTitle[5]`)_ <br> **Semester:** `r Papers$Semester[5]` <br> **Convenor:** `r Papers$Convenor[5]` <br> **Email:** `r Papers$Email[5]` <br> **Pre-Reqs:** `r Papers$PreReqs[5]` <br> **Restrictions:** `r Papers$Restrictions[5]`  

```{r MAOH201_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "MAOH 201")
assess <- make_paper_assess_info(Papers = Papers, Paper = "MAOH 201")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[6]`** <br> _(`r Papers$PaperTitle[6]`)_ <br> **Semester:** `r Papers$Semester[6]` <br> **Convenor:** `r Papers$Convenor[6]` <br> **Email:** `r Papers$Email[6]` <br> **Pre-Reqs:** `r Papers$PreReqs[6]` <br> **Restrictions:** `r Papers$Restrictions[6]`  

```{r MAOH301_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "MAOH 301")
assess <- make_paper_assess_info(Papers = Papers, Paper = "MAOH 301")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[7]`** <br> _(`r Papers$PaperTitle[7]`)_ <br> **Semester:** `r Papers$Semester[7]` <br> **Convenor:** `r Papers$Convenor[7]` <br> **Email:** `r Papers$Email[7]` <br> **Pre-Reqs:** `r Papers$PreReqs[7]` <br> **Restrictions:** `r Papers$Restrictions[11]`  

```{r PACH201_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "PACH 201")
assess <- make_paper_assess_info(Papers = Papers, Paper = "PACH 201")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[8]`** <br> _(`r Papers$PaperTitle[8]`)_ <br> **Semester:** `r Papers$Semester[8]` <br> **Convenor:** `r Papers$Convenor[8]` <br> **Email:** `r Papers$Email[8]` <br> **Pre-Reqs:** `r Papers$PreReqs[8]` <br> **Restrictions:** `r Papers$Restrictions[8]`  

```{r PACH301_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "PACH 301")
assess <- make_paper_assess_info(Papers = Papers, Paper = "PACH 301")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[9]`** <br> _(`r Papers$PaperTitle[9]`)_ <br> **Semester:** `r Papers$Semester[9]` <br> **Convenor:** `r Papers$Convenor[9]` <br> **Email:** `r Papers$Email[9]` <br> **Pre-Reqs:** `r Papers$PreReqs[9]` <br> **Restrictions:** `r Papers$Restrictions[9]`  

```{r PUBH202_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "PUBH 202")
assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 202")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[10]`** <br> _(`r Papers$PaperTitle[10]`)_ <br> **Semester:** `r Papers$Semester[10]` <br> **Convenor:** `r Papers$Convenor[10]` <br> **Email:** `r Papers$Email[10]` <br> **Pre-Reqs:** `r Papers$PreReqs[10]` <br> **Restrictions:** `r Papers$Restrictions[10]`  

```{r PUBH203_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "PUBH 203")
assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 203")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[11]`** <br> _(`r Papers$PaperTitle[11]`)_ <br> **Semester:** `r Papers$Semester[11]` <br> **Convenor:** `r Papers$Convenor[11]` <br> **Email:** `r Papers$Email[11]` <br> **Pre-Reqs:** `r Papers$PreReqs[11]` <br> **Restrictions:** `r Papers$Restrictions[11]`  

```{r PUBH204_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "PUBH 204")
assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 204")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[12]`** <br> _(`r Papers$PaperTitle[12]`)_ <br> **Semester:** `r Papers$Semester[12]` <br> **Convenor:** `r Papers$Convenor[12]` <br> **Email:** `r Papers$Email[12]` <br> **Pre-Reqs:** `r Papers$PreReqs[12]` <br> **Restrictions:** `r Papers$Restrictions[12]`  

```{r PUBH211_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "PUBH 211")
assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 204")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[13]`** <br> _(`r Papers$PaperTitle[13]`)_ <br> **Semester:** `r Papers$Semester[13]` <br> **Convenor:** `r Papers$Convenor[13]` <br> **Email:** `r Papers$Email[13]` <br> **Pre-Reqs:** `r Papers$PreReqs[13]` <br> **Restrictions:** `r Papers$Restrictions[13]`  

```{r PUBH303_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "PUBH 303")
assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 303")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[14]`** <br> _(`r Papers$PaperTitle[14]`)_ <br> **Semester:** `r Papers$Semester[14]` <br> **Convenor:** `r Papers$Convenor[14]` <br> **Email:** `r Papers$Email[14]` <br> **Pre-Reqs:** `r Papers$PreReqs[14]` <br> **Restrictions:** `r Papers$Restrictions[14]`  

```{r PUBH304_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "PUBH 304")
assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 304")
```

`r text`  

-------------------------------------  
`r assess`  

### **`r Papers$PaperCode[15]`** <br> _(`r Papers$PaperTitle[15]`)_ <br> **Semester:** `r Papers$Semester[15]` <br> **Convenor:** `r Papers$Convenor[15]` <br> **Email:** `r Papers$Email[15]` <br> **Pre-Reqs:** `r Papers$PreReqs[15]` <br> **Restrictions:** `r Papers$Restrictions[15]`  

```{r PUBH311_Paper_Learning_Objectives}
text <- make_paper_info(Papers = Papers, Paper = "PUBH 311")
assess <- make_paper_assess_info(Papers = Papers, Paper = "PUBH 311")
```

`r text`  

-------------------------------------  
`r assess`  

